RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2013-12-17 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Include an example protocol buffer definition early in the file and example code accessing it. As with everything here, still very rough.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@562 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

TODO(ms): random citations to work in:
q
We make use of Object Tables \citep{RObjectTables} for lookup.
Many sources compare data serialization formats and show protocol
buffers very favorably to the alternatives, such
as \citep{Sumaray:2012:CDS:2184751.2184810}

@@

<<>>=
library(RProtoBuf)
args( readProtoFiles )
@

@@

The \texttt{RProtoBuf} package uses the user defined tables framework
that is defined as part of the \texttt{RObjectTables} package available
from the OmegaHat project.

@@

Jeroen Ooms took a similar approach influenced by Saptarshi in his
\texttt{RProtoBufUtils} package.  Unlike Saptarshi's package,
RProtoBufUtils depends on RProtoBuf for underlying message operations.
This package is available at
\url{https://github.com/jeroenooms/RProtoBufUtils}.

@@

Its pretty useful.  Murray to see if he can get approval to talk a
tiny bit about how much its used at Google.

>>>>

\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;        // Unique ID number for person.
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1; WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2 [default = HOME];
 }
 repeated PhoneNumber phone = 4;
}
\end{example}

<<echo=TRUE>>=
library(RProtoBuf)
person <- new(tutorial.Person, id=1, name="Romain")
person$id
person$name
person$name <- "Dirk"
cat(as.character(person))
@

@@

TODO(ms): random citations to work in:

Many sources compare data serialization formats and show protocol
buffers very favorably to the alternatives, such
as \citep{Sumaray:2012:CDS:2184751.2184810}

@@

@@

The \texttt{RProtoBuf} package uses the user defined tables framework
that is defined as part of the \texttt{RObjectTables} package available
from the OmegaHat project \citep{RObjectTables}.

@@

Jeroen Ooms took a similar approach influenced by Saptarshi in his
\pkg{RProtoBufUtils} package.  Unlike Saptarshi's package,
RProtoBufUtils depends on RProtoBuf for underlying message operations.
This package is available at
\url{https://github.com/jeroenooms/RProtoBufUtils}.

@@

%Its pretty useful.  Murray to see if he can get approval to talk a
%tiny bit about how much its used at Google.
